Video-Agnostic Perturbations: Efficient Targeted Attacks for Siamese Visual Tracking

### 2021-04-18 博士/论文提交/adversarial_attack/TCSVT/latex/bare_jrnl.tex
正文增至8页

\textit{Ablation Study: Influence of Training Loss} We implement a series of experiments to analyse and evaluate the contribution of each loss component.
In Table \ref{tab:loss}, we report our results on GOT-Val with respect to different perturbations trained with different combinations of loss terms in Equ. \ref{eq:loss}.
To summarize, all the loss terms are beneficial whereas the classification term is more important than the quality assessment term for attacking.

\textit{Ablation Study: Influence of Training Iterations} As shown in Table \ref{tab:iter}, after around 30000 training iterations, the generated perturbations can fool most targets in GOT-Val. The AO with respect to the \textit{real trajectory} falls down from 0.760 to 0.035. We notice that at the start of training period (when training iteration number is less than 2048), the decreasing of AO is significantly faster than in the later period. This demonstrates the fast convergence ability of our end-to-end training pipeline while generating the adversarial perturbations.

@@

We compare the attack performance of our method with the recent promising attack approaches, \ie, the untargeted attack method CSA \cite{CSA} based on AlexNet and two other targeted attack methods FAN \cite{FAN} based on AlexNet and TTP \cite{TTP} based on ResNet-50.
We report the precision score with respect to the \textit{real / fake trajectory} in Table \ref{tab:untargeted}.
Our method significantly outperforms other methods at no additional cost except the mere addition and pasting operations -- and does not require gradient optimization or network inference.

>>>>

\textit{Ablation Study: Influence of Training Iterations} Table \ref{tab:iter} demonstrates the effect of the number of training iterations of the algorithm on the effectiveness of the attack. It can be observed that as the number of iterations increases, the AO value relative to the false trajectory increases significantly, while the AO value relative to the real trajectory decreases significantly. This demonstrates the effectiveness of the end-to-end training process proposed in this chapter.
After about 30,000 training iterations, the resulting perturbation prevents the tracker from tracking most of the targets in GOT-Val, and the AO relative to the true trajectory decreases from 0.760 to 0.035.
We note that the AO decreases significantly faster at the beginning of the training cycle (training iterations less than 2048) than later. This demonstrates the fast convergence capability of our end-to-end training scheme.

To verify whether the perturbations generated for the template images are difficult to perceive, we evaluate and analyze the quality of the template images after the perturbations. The quality of the perturbed template images is evaluated by the metric SSIM. As shown in Table \ref{tab:iter}, the SSIM value of the perturbed template image gradually decreases as the training proceeds, which indicates that the difference between the perturbed template image and the original template image gradually increases due to the learned adversarial perturbation being added to the clean template image. The SSIM value ranges from 0 to 1. If the SSIM is close to 1, the difference between the perturbed template image and the original template image is smaller. If SSIM is closer to 0, it means that the difference between the perturbed template image and the original template image is larger, which means that the perturbation generated by the template image is easier to perceive. The SSIM value after convergence of this algorithm is 0.88, which means that the difference between the perturbed template image and the original template image is smaller, that is, the perturbation generated by the template image is harder to perceive (see Fig. \ref{fig:1}).

\textit{Ablation Study: Influence of Training Loss} We implemented a series of experiments to analyze and evaluate the contribution of each loss component.
In table \ref{tab:loss}, we report the attack results on the GOT-Val dataset. The results reflect the differences in attack performance for different perturbations obtained by training using different combinations of the loss terms in Eq. \ref{eq:loss}.
The AO value of the tracker relative to the true trajectory decreases from 0.760 to 0.703 when only adversarial information is generated using quality assessment loss, indicating that quality assessment loss can cause a slight degradation in the performance of the tracker. This is because the perturbation information generated using quality assessment loss interferes with the tracker's ability to select the best target frame.
However, the tracker's AO value relative to the spurious trajectory is only 0.044, indicating that the perturbations generated using quality assessment loss alone can barely cause the tracker to generate tracking frames along the specified trajectory.
When only the adversarial information is generated using regression loss, the AO value of the tracker relative to the true trajectory decreases from 0.760 to 0.165, indicating that regression loss can cause a large degradation in the tracker's performance. This is because the perturbation information generated using regression loss corrupts the tracker's ability to predict the true target border position.
When only adversarial information is generated using classification loss, the tracker's AO value decreases from 0.760 to 0.086 relative to the true trajectory and up to 0.718 relative to the false trajectory. this is because the perturbation information generated using classification loss causes the tracker to localize to the false target instead of the true target's location.
In conclusion, all loss terms are beneficial, and the classification term is more important than the quality assessment term.

@@

We compare the twin network attack method proposed in this chapter with the latest attack methods, including the AlexNet-based untargeted attack method CSA \cite{CSA}, and two other targeted attack methods: the AlexNet-based FAN \cite{FAN} and the ResNet50 -based TTP \ cite{TTP}. We report the accuracy scores relative to the real/false trajectories in table \ref{tab:untargeted}. CSA \cite{CSA} is a twin tracking attack method called cooling-shrinking attack. CSA can suppress the peak region on the heat map reflecting the target location, which is used to attack the tracker's targeting ability; CSA can also simultaneously force the tracker's predicted bounding box to shrink, which is used to attack the tracker's the border regression capability of the tracker. However, the method requires running a generative network for each frame to obtain adversarial information, so the attack time is as high as 4720 ms, making it difficult to meet the demand for real-time tracking. CSA reduces the accuracy score relative to the real trajectory from 0.851 to 0.458, and the attack performance is more limited. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for target tracking. In the literature \cite{FAN}, Liang et al. proposed a fast attack network (FAN) for attacking SiamFC trackers. To perform untargeted attacks, the FAN proposes a drift loss that shifts the tracker's prediction of the target's position. Over time, the tracking error accumulates until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of a particular trajectory region.FAN can reduce the accuracy score relative to the real trajectory from 0.720 to 0.180, which has better performance for non-targeted attacks. However, the accuracy score is only 0.420 with respect to false trajectories, which has a more limited targeted attack performance. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. In the literature \cite{TTP}, Nakka et al. propose a temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker.TTP generates a single adversarial perturbation from the template image only and adds this perturbation to each search image of the video TTP reduces the accuracy score relative to the real trajectory from 0.910 to 0.080, which has a better performance for non-targeted attacks. However, the accuracy score of this method is only 0.692 with respect to the false trajectory, and the performance of targeted attacks is more limited. In addition, the method needs to run a generative network for each video to obtain adversarial information, and thus requires the computational and storage resources of the target tracking platform, which is difficult to deploy to resource-constrained embedded platforms. Our method can reduce the accuracy score from 0.861 to 0.048 with respect to real trajectories and up to 0.928 with respect to false trajectories, which is significantly better than other methods, and only needs to perform additive operations and image paste operations to generate adversarial information for any video without gradient optimization or network inference.

Translated with www.DeepL.com/Translator (free version)
